A Reduced Order Model for Porous Media Flows: Coupling Linear Regression with Principal Component Analysis (PCA) using High-Order Singular Value Decomposition (HOSVD) in Upscaling Calculations for Permeability in Reservoir Simulations

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

With respect to the PDFCase and for this specific resolution, it is important to note that Fig.~\ref{fig:PermFields}(e) is only one realiztion of infinitely many possible representations of the PDFCase. Meanwhile, the PCA-LinReg Case will retain this specific (\ie Fig.~\ref{fig:PermFields}(e)) permeability field for this specific resolution (\ie if linear interpolation is used, but this digresses from the main point and will be discussed in future work). Therefore, the permeability value at a specific point in the PDFCase is not directly related to the data value at the nearest point in the BaseCase because the randomly generated PDF dataset is also randomly arranged within each block. However, the data value at a point in the PCA-LinReg Case is directly related to the nearest data values with respect to the same point in the BaseCase, throught the interpolation which takes place in the PCS.

Furthermore, prior to the pre-processing required for evaluating the ArithMeanCase, HarmMeanCase and the PDFCase it is necessary to have an understanding of the whole domain and pre-define blocks with similar properties (\ie blocks $K1,~K2,~K3$ and $K4$) in this case. However, with the PCA-LinReg Case, knowledge of blocks with similar properties is not required prior to the upscaling. Albeit, one has to select the upgrid resolution carefully, if the resolution is too large then there is the risk of losing relevant data in the interpolation. The limits of the techniques used for the PCA-LinReg Case will be discussed in the author's future work.

>>>>

\medskip
With respect to the PDFCase and for this specific resolution, it is important to note that Fig.~\ref{fig:PermFields}(e) is only one realiztion of infinitely many possible representations of the PDFCase. Meanwhile, the PCA-LinReg Case will retain this specific permeability distribution (\ie Fig.~\ref{fig:PermFields}(e)) for such mesh resolution (\ie if linear interpolation is used, but this digresses from the aim of this work and it will be discussed in future publications). Therefore, the permeability value at a specific point in the PDFCase is not directly related to the data value at the nearest point in the BaseCase because the randomly generated PDF dataset is also randomly arranged within each block. However, the data value at a point in the PCA-LinReg Case is directly related to the nearest data values with respect to the same point in the BaseCase, throught the interpolation which takes place in the PCS.

\medskip
Furthermore, prior to the pre-processing required for evaluating the ArithMeanCase, HarmMeanCase and the PDFCase it is necessary to have an understanding of the whole domain and pre-define blocks with similar properties (\ie blocks $K1,~K2,~K3$ and $K4$) in this case. However, with the PCA-LinReg Case, knowledge of blocks with similar properties is not required prior to the upscaling. Albeit, one has to select the upgrid resolution carefully, if the resolution is too large then there is the risk of losing relevant data in the interpolation. The limits of the techniques used for the PCA-LinReg Case will be discussed in the author's future work.
